MSOA Industrial Electricty and Gas maps

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Fixing some of the errors

```{r Creating the mean electricty consumption from the industrial sector MOSA}
ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
merged_nondomelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndelec)
merged_ndelec$ndelec_diff<-as.numeric(merged_ndelec$ndelec2019) - as.numeric(merged_ndelec$ndelec2010) ##BROKEN
summary(merged_ndelec)
```
```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019) +
  geom_sf(aes(fill=" Mean consumption (kWh per meter)"))+ 
  scale_fill_continuous(name="Change in mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```

>>>>

```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019) +
  geom_sf(aes(fill=" Mean consumption (kWh per meter)"))+ 
  scale_fill_continuous(name="Change in mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```
